Breast Cancer Diagnosis Classification Analysis

### 2022-12-09 ethan_temp_powerpoint.rmd

>>>>

## Regression Analysis: Ethan
```{r}
dataTemp <- read.csv("breast_cancer_diagnostic_data.csv")
dataTot <- dataTemp %>% select_if(~ !any(is.na(.)))
testTot <- read.csv("test.csv")
trainingTot <- read.csv("training.csv")

dataE <- data
corr_df <- dataE[,c('area_worst', 'area_mean', 'concave.points_mean', 'radius_worst')]
ggpairs(corr_df)
```
-Test

### 2022-12-09 powerpoint.rmd

```{r, fig.height=8, fig.width=12}
source("Danny's Analysis.R", echo = F, local = T)

train[,c(1,2,12,22)] |>
  ggpairs(title = "Correlation b/w Radius Measurements")
```

@@

>>>>

```{r, fig.height=6, fig.width=8}
source("PPTX-code.R", echo = F, local = T)

```

@@

- LogReg
- KNN
- QDA
- RF
- xGBoost
- SVC
- Lower prediction cutoff to account for Type II Error

## K-Nearest Neigbors Model

- Tuned neighbors value
- 2 False-Negatives
- 96.04% prediction accuracy

## Support Vector Classifier Model

- Tuned cost value
- 2 False-Negatives
- 96.48% prediction accuracy

## Random Forest Model

- 1 False-Negative
- 95.15% prediction accuracy
